---
title: "post_processing_wa"
author: "Michael Spencer"
date: "10/23/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Cleaning half-processed data that was retrieved via the opp processing script. Errors in the script meant running it gave data that has yet to clean enforcements or violations, and has not been sanitized. In this script, we aim to do just that, ideally replicating what the opp processing script would have done had errors not occured. This document will be made into a R script for quicker processing since the dataset is fairly slow locally.

Altered opp scripts include:

* wa/statewide.R (circumvented violation, enforcement, and calculated columns processing)
* standardize.R (circumvented schema columns, enforcing types, predicate correction, all santizing)
* opp.R and utils.R added print statements

## Setup

### Libraries
```{r}
if (!require(tidyverse)) install.packages("tidyverse")
library(tidyverse)
```

### Parameters
```{r}
path_data <- paste0(here::here(), "/data")
path_data_states <- paste0(path_data, "/states")
```

### Load Data
```{r}
# source("post_processing_wa.R")

#Loads half processed data that came from running modified opp script
data_wa_raw <-
	paste0(path_data_states, "/wa/statewide_sample.rds") %>%
	read_rds()
```

### Functions
```{r}
first_of <- function(..., default = NA) {
  tbl <- cbind(..., "__default" = TRUE)
  nms <- colnames(tbl)
  v <- nms[apply(tbl, 1, which.max)]
  str_replace(v, "__default", as.character(default))
}
```


## Clean Data

### Clean Enforcements
```{r}
data_wa_raw %>% 
	unite("all_enforcements", starts_with("enforcement_"), sep = ",") %>% 
	mutate(
		all_enforcements_big = str_replace_all(all_enforcements, pattern = "NA|,", ""),
		raw_driver_race_big = case_when(
			raw_driver_race == "1" ~ "white",
	    raw_driver_race == "2" ~ "black",
	    raw_driver_race == "3" ~ "native american",
	    raw_driver_race == "4" ~ "Asian", # Asian
	    raw_driver_race == "5" ~ "pacific islander", # Pacific Islander
	    raw_driver_race == "6" ~ "east indian", # East Indian
	    raw_driver_race == "7" ~ "hispanic",
	    raw_driver_race == "8" ~ "other" # Other
		),
		stop_reason_big = case_when(
			raw_contact_type == "01"  ~ 'Self-Initiated Contact',
	  	raw_contact_type == "02"  ~ 'Calls for service',
	  	raw_contact_type == "04"  ~ 'Collisions',
	  	raw_contact_type == "05"  ~ 'Collisions enf. follow-up',
	  	raw_contact_type == "06"  ~ 'Other enf. follow-up',
	  	raw_contact_type == "07"  ~ 'Aggressive driving',
	  	raw_contact_type == "08"  ~ 'Road rage',
	  	raw_contact_type == "09"  ~ 'Emphasis patrol',
	  	raw_contact_type == "10"  ~ 'CMV inspect/weighing',
	  	raw_contact_type == "12"  ~ 'Self-Initiated Physical Assist',
	  	raw_contact_type == "13"  ~ 'Distracted driving',
	  	raw_contact_type == "20"  ~ NA_character_
		)
	) %>% 
		mutate_at(
	 		vars(starts_with("violation_")),
	 		~case_when(
		    . == "1"    ~ "DUI - With test",
				. == "10"   ~ "Right of way",
				. == "100"  ~ "Smoke Marijuana Public",
				. == "101"  ~ "DUI - Drugs W/Test",
				. == "102"  ~ "DUI - Drugs No Test",
				. == "103"  ~ "DUI - Under Age W/Test",
				. == "104"  ~ "DUI - Under Age No Test",
				. == "105"  ~ "Alcohol in Sys W/Test",
				. == "106"  ~ "Alcohol in Sys W/O Test",
				. == "107"  ~ "Interlock Device (DUI)",
				. == "108"  ~ "Veh Hom - DUI/Drug",
				. == "109"  ~ "Veh Assault - DUI/Drug",
				. == "11"   ~ "Centerline",
				. == "110"  ~ "Move Over Law",
				. == "112"  ~ "Left Lane Travel",
				. == "12"   ~ "Lane Travel",
				. == "13"   ~ "Shoulder",
				. == "14"   ~ "Divider/Barrier",
				. == "148"  ~ "Intermediate Driver Liscence",
				. == "149"  ~ "Out of state vehicle lic.",
				. == "15"   ~ "Passing",
				. == "150"  ~ "Oper Liscence - C",
				. == "151"  ~ "Vehicle Lic (tabs/plates)",
				. == "152"  ~ "Vehicle registration (paper)",
				. == "153"  ~ "Debris - Thrown",
				. == "154"  ~ "Debris - Lighted",
				. == "155"  ~ "Over Llgl Gross",
				. == "156"  ~ "Over Axle",
				. == "157"  ~ "Over Tires",
				. == "158"  ~ "Over Lic Capacity",
				. == "159"  ~ "Valid Tonnage",
				. == "16"   ~ "Signal",
				. == "160"  ~ "Over Length",
				. == "161"  ~ "Over Width",
				. == "162"  ~ "Over Height",
				. == "163"  ~ "Use Fuel",
				. == "164"  ~ "Permit:  Spec - None",
				. == "165"  ~ "Permit:  Spec - Size",
				. == "166"  ~ "Permit:  Spec - Wght",
				. == "167"  ~ "Over Axle Spcng",
				. == "168"  ~ "Over Lgl & Pmt AT",
				. == "169"  ~ "Over Lgl & Pmt LT",
				. == "17"   ~ "Turning",
				. == "170"  ~ "Permit:  Forest",
				. == "171"  ~ "Permit:  Comn Carr",
				. == "173"  ~ "Child Restraint",
				. == "174"  ~ "Safety Belt",
				. == "175"  ~ "HOV Violations",
				. == "176"  ~ "Parking/Campus",
				. == "177"  ~ "Trip Permit - None",
				. == "178"  ~ "License Susp/Rev 1st Deg",
				. == "179"  ~ "Failiure to Appear",
				. == "18"   ~ "Stop Sign",
				. == "180"  ~ "Medical Certificate",
				. == "181"  ~ "Oper Licence - I",
				. == "182"  ~ "Insurance - None",
				. == "183"  ~ "M/C Helmet",
				. == "184"  ~ "License Susp/Rev 2nd Deg",
				. == "185"  ~ "License Susp/Rev 3rd Deg",
				. == "186"  ~ "Habitual Traffic Offender",
				. == "187"  ~ "M/C Endorsement",
				. == "19"   ~ "Traffic Light",
				. == "198"  ~ "Other Non-Hazd/I",
				. == "199"  ~ "OtherNon-Hazd/C",
				. == "2"    ~ "DUI - W/O Test",
				. == "20"   ~ "Restrictive Sign",
				. == "200"  ~ "Business Inspections",
				. == "201"  ~ "Vehicle Dealer",
				. == "202"  ~ "Aircraft Registration",
				. == "203"  ~ "Hulk Hauler",
				. == "204"  ~ "Scrap Processor",
				. == "205"  ~ "Tow Truck Company",
				. == "206"  ~ "Fuel System",
				. == "207"  ~ "Suspension System",
				. == "21"   ~ "Headlights Dim",
				. == "22"   ~ "Light Violations",
				. == "23"   ~ "Headlights - None",
				. == "24"   ~ "Log Book - Prv Carr",
				. == "25"   ~ "Secure Load",
				. == "26"   ~ "Brakes",
				. == "27"   ~ "Steering",
				. == "28"   ~ "Tires",
				. == "29"   ~ "Exhaust",
				. == "3"    ~ "Neg Driving - 1st Degree",
				. == "30"   ~ "Excessive Smoke",
				. == "301"  ~ "Fail to Obtain WA Driver License",
				. == "31"   ~ "Other Def Equipment",
				. == "32"   ~ "Parking Viol",
				. == "33"   ~ "Pedestrian Viol",
				. == "34"   ~ "Bicycle Violations",
				. == "35"   ~ "Hitchhiking",
				. == "36"   ~ "RR Crossing",
				. == "37"   ~ "Lane Change",
				. == "38"   ~ "Backing",
				. == "39"   ~ "Log Book - Reg Carr",
				. == "4"    ~ "Speed",
				. == "40"   ~ "Wheels",
				. == "41"   ~ "Frame",
				. == "42"   ~ "Coupling",
				. == "43"   ~ "Warning Device",
				. == "44"   ~ "Debris - Escape",
				. == "45"   ~ "Uncovered Load",
				. == "46"   ~ "Reckless Driving",
				. == "47"   ~ "Hit and run",
				. == "48"   ~ "Vehicle Homicide",
				. == "49"   ~ "Vehicular Assault",
				. == "5"    ~ "Speed - Aircraft",
				. == "50"   ~ "HOV Hot lane",
				. == "51"   ~ "Hazmat Violations",
				. == "52"   ~ "Toll evasion",
				. == "53"   ~ "Neg Driving - 2nd Degree",
				. == "54"   ~ "Cell phone - Text",
				. == "55"   ~ "Cell phone - Handheld",
				. == "6"    ~ "Speed - Radar",
				. == "60"   ~ "Fail to Carry Chains",
				. == "61"   ~ "Fail to Chain",
				. == "62"   ~ "Burglary",
				. == "63"   ~ "Danger Weapons",
				. == "64"   ~ "Disorderly Conduct",
				. == "65"   ~ "Drink in public",
				. == "66"   ~ "Harassment - Felony",
				. == "67"   ~ "Harassment - Misdemeanor",
				. == "68"   ~ "Identity Theft",
				. == "69"   ~ "Indecent Exposure - Felony",
				. == "7"    ~ "Speed - Too fast",
				. == "70"   ~ "Indecent Exposure - Misdemeanor",
				. == "71"   ~ "Intimid Pub Serv - Felony",
				. == "72"   ~ "No contct/Rest Order - Felony",
				. == "73"   ~ "No contct/Rest Order - Misdemeanor",
				. == "74"   ~ "Obstructing",
				. == "75"   ~ "Physical Assault - Felony",
				. == "76"   ~ "Physical Assault - Misdemeanor",
				. == "77"   ~ "Pos Stolen Prop - Felony",
				. == "78"   ~ "Pos Stolen Prop - Misdemeanor",
				. == "79"   ~ "Skateboarding",
				. == "8"    ~ "Impeding Traffic",
				. == "80"   ~ "Theft - Felony",
				. == "81"   ~ "Theft - Misdemeanor",
				. == "82"   ~ "Trespassing",
				. == "83"   ~ "Vandalism - Felony",
				. == "84"   ~ "Vandalism - Misdemeanor",
				. == "85"   ~ "Vehicle Prowl - Felony",
				. == "86"   ~ "Vehicle Prowl - Misdemeanor",
				. == "87"   ~ "Fail to Disperse",
				. == "88"   ~ "Riot - Felony",
				. == "89"   ~ "Riot - Misdemeanor",
				. == "897"  ~ "Redeem Impound",
				. == "9"    ~ "Follow close",
				. == "90"   ~ "Domestic Viol - Felony",
				. == "900"  ~ "Open Container",
				. == "901"  ~ "Minor in possession",
				. == "902"  ~ "Liquor to Minor",
				. == "903"  ~ "Vehicle theft",
				. == "904"  ~ "Drugs - Felony",
				. == "905"  ~ "Felony Flight - Elude",
				. == "906"  ~ "Misdemeanor Warrant",
				. == "907"  ~ "Felony Warrant",
				. == "908"  ~ "Drugs - Misdemeanor",
				. == "909"  ~ "Stolen Veh. Recovered",
				. == "91"   ~ "Domestic Viol - Misdemeanor",
				. == "910"  ~ "Weapons Violation - Felony",
				. == "911"  ~ "Weapons Violation - Misdemeanor",
				. == "914"  ~ "Drugs Paraphernalia - Felony",
				. == "918"  ~ "Drugs Paraphernalia - Misdemeanor",
				. == "997"  ~ "Non-Traffic Vltn/I",
				. == "998"  ~ "Non-Traffic Vltn/C",
				. == "999"  ~ "Non-Traffic Vltn/F",
				. == "98"   ~ "Other violations - I",
				. == "99"   ~ "Other violations - C"
			)
	) %>% 
	unite("all_violations", starts_with("violation_"), sep = ",") %>% 
	mutate(
		all_violations_big = 
			str_replace_all(all_violations, pattern = "NA", replacement = "") %>% 
			str_replace_all(pattern = "^,+|,+$", replacement = ""),
		arrest_made_big = str_detect(all_enforcements_big, "1"),
		citation_issued_big = str_detect(all_enforcements_big, "1"),
		warning_issued_big = str_detect(all_enforcements_big, "2|3"),
		outcome_big = first_of(
      "citation" = citation_issued_big,
      "warning" = warning_issued_big
		)
	) %>% 
	select(
		-employee_first,
		-employee_last,
		-officer_first_name,
		-officer_last_name,
		-raw_officer_race,
		-raw_officer_gender,
		-contact_date,
		-contact_hour,
		-highway_type.x,
		-road_number.x,
		-milepost.x,
		-raw_contact_type,
		-raw_driver_race,
		-driver_age,
		-raw_driver_gender,
		-raw_search_type,
		-X1,
		-milepost.y,
		-road_number.y,
		-highway_type.y,
		-all_violations,
		-all_enforcements,
		-stop_reason,
		-arrest_made,
		-citation_issued,
		-warning_issued,
		-outcome,
		-location
	) %>% 
	select(
		raw_row_number,
		date,
		time,
		longitude = "lng",
		latitude = "lat",
		county_fips,
		county_name,
		officer_race,
		officer_sex,
		department_name,
		type,
		stop_reason_big,
		all_enforcements_big,
		all_violations_big,
		subject_race,
		raw_subject_race_big = "raw_driver_race_big",
		subject_sex,
		subject_age,
		contraband_found,
		frisk_performed,
		search_basis,
		search_conducted,
		arrest_made_big,
		outcome_big
	) %>% 
	View()
```